\cvsection{Education}
\begin{cventries}
	\cventry
	{Machine Learning and Data Mining Master's Degree}
	{University of Jean Monnet}
	{Saint-\'{E}tienne, France}
	{Sep. 2017 - Sep. 2019}
	{
		\begin{cvitems}
			\item{Key modules include:}
			\setlength\multicolsep{0pt}
			\begin{multicols}{3}
				\item{Optimisation \& Operational Research}
				\item{Introduction to Machine Learning}
				\item{Algorithms}
				\item{Complexity}
				\item{Data Analysis}
				\item{Data Mining}
			\end{multicols}
		\end{cvitems}
	}
	
	\cventry
    {BSc Hons 2:1 Physics with Foundation Year}
    {University of Sussex}
    {Brighton, UK}
    {Sept 2013 - Jun 2017}
    {
      \begin{cvitems}
      \item{Received Eliahou Dangloor Scholarship for academic excellence.}
      \item{Key modules include:}
      \setlength\multicolsep{0pt}
      \begin{multicols}{3}
        \item{Final Year ML project - 66\% }
        \item{Skills in Physics - 72\%}
        \item{Extragalatic Astronomy - 78\%}
        \item{Scientific Computing - 69\%}
        \item{Electrodynamics - 70\%}
        \item{Physics Laboratory - 72\%}
      \end{multicols}
      \end{cvitems}
    }
    
	\cventry
	{International Summer School}
	{Hong Kong University of Science \& Technology}
	{Hong Kong}
	{Summer 2015}
	{
		\begin{cvitems}
			\item {Studied Electro-robot Design, learning to design and build a robot from elementary components that could sense and navigate itself around a course. Our team won the award for best robot.}
			\item {Studied Business Statistics, improving my ability to handle statistics in real-world applications.}
			\item {Worked with students from around the world and lived and studied in a very different culture.}
		\end{cvitems}
	}
	
  \cventry
    {A/As Levels}
    {Esher College}
    {Esher, UK}
    {2006 - 2009}
    { 
    \begin{cvitems}
    \setlength\multicolsep{0pt}
      \begin{multicols}{3}
      \item{Physics - A}
      \item{Chemistry - A}
      \item{Biology - A}
      \item{English Lit. - A}
      \item{Maths As Level - A}
      \item{Classic Civ. As Level - C}
      \end{multicols}
      \end{cvitems}
    }
    
  \cventry
    {GCSE's}
    {Tiffin Grammar School}
    {Kingston, UK}
    {2001 - 2006}
    {
    \begin{cvitems}
      \item{9 A - C's including Maths, English and Triple Science}
      \end{cvitems}
    }
\end{cventries}
