\cvsection{Relevant Experience}
\begin{cventries}
	\cventry
	{University of Jean Monnet}
	{Project to Detect Subtitles from Audioto Synchronise Subtitle Track in Real Time}
	{Saint-\'{E}tienne, France}
	{May 2018 - Jul. 2018}
	{
		\begin{cvitems}
			\item {Extracted MFCC's to use as predictive feature.}
			\item {Implemented CNN's, tuned with hyperopt and improved architecture to obtain 93\% accuracy.}
			\item {Implemented an informed search method to locate position in track based on audio features.}
		\end{cvitems}
	}
  \cventry
    {University of Sussex}
    {Final Year Project in Identifying Fast and Slow Rotating Galaxies Using Machine-Learning Algorithms}
    {Brighton, UK}
    {2016 - 2017}
    {
      \begin{cvitems}
        \item {Located, downloaded and processed astronomical data using get scripts and FITS files within Python and Linux.}
        \item {Implemented Decision Trees and Random Forests modules from the Scikit-Learn package within Python.}
        \item {Achieved grade of 80\% when presenting preliminary results.}
      \end{cvitems}
    }
  \cventry
    {University of Sussex}
    {UKSEDS (Students for the Exploration \& Development of Space) Branch Founder and President}
    {Brighton, UK}
    {2014 - 2017}
    {
      \begin{cvitems}
        \item {Founded the first branch at Sussex University, increasing membership to 20 members after achieving £400 request.}
        \item {Won the Thales Arduino challenge within the university using programming and electrical skills.}
        \item {Organised visits to National Student Space conference, Graduate Space Fairs, the Cosmonaut Exhibition and rocket building events.}
      \end{cvitems}
    }
\end{cventries}
